Output Summary

### 2023-08-17 03-post-process/output-plots-children/10-rho-params.Rmd
Improve Rho parameter Rmd section

# assign names to the different rho parameters
rho_labels = c(
  "rho_Lphi_E_Pb" = "Egg-to-Parr Survival",
  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
  "rho_Lphi_Mb_Ma" = "Trib. to LGR Survival",
  "rho_lL_Pb" = "Mean Parr Length",
  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
  "rho_Lphi_Rb_Ra" = "BON -> LGR Survival",
  "rho_Lpi" = "Pr(Fall Migrant)",
  "rho_Lphi_Ma_O0" = "LGR -> Ocean Survival"
)
```

@@

* Main: Mean correlation of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 95% CRI)
* Dots: Posterior mean correlation of individual population pairs
<!-- * Grey: Prior distribution (95%, 80%, and 50% CRIs in increasing darkness) -->

@@

### Egg-to-Parr Survival

@@

### Trib. to LGR Survival

@@

### LGR to Ocean Survival

@@

#### Pr(Age-3)

@@

#### Pr(Age-4)

@@

### BON to LGR Survival

>>>>

# assign names to the different rho parameters
rho_labels = c(
  "rho_Lphi_E_Pb" = "Egg \u2192 Parr Survival",
  "rho_Lphi_O0_O1" = "Yr1 Ocean Survival",
  "rho_Lpsi_O1" = "Pr(Mature Age-3)",
  "rho_Lpsi_O2" = "Pr(Mature Age-4)",
  "rho_lDelta_L_Pb_Mb" = "'Growth' Factor",
  "rho_Lphi_Mb_Ma" = "Smolt \u2192 LGR Survival",
  "rho_lL_Pb" = "Mean Parr Length",
  "rho_Lphi_Pa_Mb" = "Overwinter Survival",
  "rho_Lphi_Rb_Ra" = "BON \u2192 LGR Survival",
  "rho_Lpi" = "Pr(Fall Migrant)",
  "rho_Lphi_Ma_O0" = "LGR \u2192 Ocean Survival"
)
```

@@

* Main: Mean correlation of all population pairs ("+" = posterior mean, thick lines = 50% CRI, thin lines = 95% CRI)
* Dots: Posterior mean correlation of individual population pairs

@@

### Egg $\to$ Parr Survival

@@

### Smolt $\to$ LGR Survival

@@

### LGR $\to$ BON Survival

@@

#### Pr(Age-3) {-}

@@

#### Pr(Age-4) {-}

@@

### BON $\to$ LGR Survival
